\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-04-30 futurework.tex
Add images

@@

With either method, in order to mitigate exponential explosion of tree size, it would probably be best to only allow the decision point set size to increase by one each iteration. An iteration framework could explore using different combinations/subsets of such, using a workqueue model, and using heuristics to identify which decision points are most useful and should be used first.

>>>>

\begin{figure*}[h]
	\begin{center}
	\includegraphics[width=0.75\textwidth]{wont-modify-vail.jpg}
	\end{center}
	\caption{Ex-members of 15-410 course staff lament the difficulty involved in teaching students concurrency debugging skills.}
\end{figure*}

@@

In Section~\ref{sec:discussion-strategies}, we recommend a strategy for an iteration framework to effectively explore trees with multiple different sets of decision points, while not knowing ahead of time which, if any, may contain a bug.
